---
title: "High School Performance and Future Salary, by College"
description: |
  Some people like to tell stressed-out students that grades aren't super important. However, for those who are intensely focused on their future careers, maybe working to get an A on that test or being at the top of your class will be worthwhile.
site: distill::distill_website
---

```{r setup, layout = "l-body-outset", include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggthemes)
library(knitr)
library(rmarkdown)
library(gt)
library(plotly)
library(dplyr)

college_data <- read_csv("rawdata/College_Data.csv")
salary_by_degree <- read_csv("rawdata/degrees-that-pay-back.csv")
salary_by_college <- read_csv("rawdata/salaries-by-college-type.csv")
salary_by_region <- read_csv("rawdata/salaries-by-region.csv")
```

*These graphs are interactive! Click around on them as much as you'd like.*
```{r, cleaning}
college_data_clean <- college_data %>%
  rename(college = X1) %>%
  select(college, Top10perc)

salary_by_region_clean <- salary_by_region %>%
  select("School Name", "Mid-Career Median Salary")

salary_by_college_clean <- salary_by_college %>%
  select("School Name", "Mid-Career Median Salary")

salary_by_college_full <- left_join(salary_by_region_clean, salary_by_college_clean, by = "School Name") %>%
  select("School Name", "Mid-Career Median Salary.x") %>%
  rename(college = "School Name", median_salary_mid_career = "Mid-Career Median Salary.x") %>%
  drop_na()

college_top10_salary <- left_join(college_data_clean, salary_by_college_full, by = "college") %>%
  drop_na() %>%
  arrange(desc(Top10perc))

college_top10_salary$median_salary_mid_career <- as.numeric(gsub('[$,]', '', college_top10_salary$median_salary_mid_career))

college_top10_salary_gpa <- college_top10_salary %>%
  slice(-c(71, 82, 84)) %>%
  add_column(avg_gpa = c(3.96, 3.95, 3.94, 4.04, 3.87, 3.95, 3.94, 3.95, 3.92, 3.90, 3.91, 3.94, 3.86, 3.91, 3.91, 3.90, 3.93, 3.80, 3.90, 3.86, 3.89, 3.76, 3.82, 3.87, 3.40, 3.86, 3.89, 3.80, 3.60, 3.92, 3.85, 3.50, 3.75, 3.57, 3.54, 3.74, 3.90, 3.50, 3.64, 3.81, 3.59, 3.74, 3.65, 3.40, 3.40, 3.80, 3.87, 3.81, 4.18, 3.30, 3.66, 3.74, 3.46, 3.63, 3.49, 3.74, 3.60, 3.59, 3.73, 3.69, 3.59, 3.86, 3.42, 3.62, 3.53, 3.58, 3.60, 3.55, 3.60, 3.50, 3.51, 3.76, 3.50, 3.60, 3.50, 3.40, 3.60, 3.54, 3.50, 3.29, 3.42, 3.57, 4.05, 3.37, 3.48, 3.30, 3.66, 3.50, 3.21, 3.91, 3.30, 3.60, 3.30, 3.00, 3.10, 3.67, 3.36, 3.21, 3.23, 2.70, 3.34, 2.99))
# Data acquired from collegesimply.com, which got its data from Wintergreen Orchard House and IPEDS; and also from prepscholar.com

college_top10_salary_gpa_plot <- college_top10_salary_gpa %>%
  ggplot(mapping = aes(x = Top10perc,
                       y = median_salary_mid_career,
                       text = college)) +
    geom_point(aes(color = Top10perc)) +
    labs(title = "High School Performance and Future Salary, by ranking",
         x = "Percent of students who were in the top 10% at their high school",
         y = "Mid-Career Median Salary") +
    geom_smooth(formula = y ~ x,
                method = "lm")
ggplotly(college_top10_salary_gpa_plot)

college_top10_salary_gpa_plot2 <- college_top10_salary_gpa %>%
  ggplot(mapping = aes(x = avg_gpa,
                       y = median_salary_mid_career,
                       text = college,
                       color = avg_gpa)) +
    geom_point() +
    labs(title = "High School Performance and Future Salary, by GPA",
         x = "Average high school GPA of undergraduates (out of 4.0)",
         y = "Mid-Career Median Salary")
ggplotly(college_top10_salary_gpa_plot2)
```

## Overall Trend
Universities that are considered the most prestigious (*e.g. Harvard, Yale, Princeton*) are more often than not in the top-right corner for both of these graphs. This means that the overwhelming majority of their students have insanely high GPAs, were at the very top of their class, and will be making the most salary mid-career.

**The plots are somewhat linear, which suggests that there is a weak correlation between high school performance, and future salary.**